Incentivizing Exploration by Heterogeneous Users

### 2018-02-17 algorithm.tex
more minor edits to section 4

To capture the probability masses of problematic agents,
we define the quantity
$\AlmostTied{\delta} = \Prob[\AgV \sim \AgentDist]{%
\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \delta}$
to be the total probability mass (across all arms) of agents
whose (actual) preference for their best arm over their second-best
arm is at most $\delta$.
\dkcomment{We should stress somewhere that we assume that actual ties
  have measure 0.}

@@

We begin by bounding the length of any phase, which will be useful to bound
the cumulative regret of the early rounds
(before tail bounds have kicked in). We prove Lemma~\ref{lem:phase-length} in the Appendix~\ref{sec:lemma4-proof}.

>>>>

\pfcomment{I deleted here we now define $q(z)$ in section 2}
\pfdelete{
To capture the probability masses of problematic agents,
we define the quantity
$\AlmostTied{\delta} = \Prob[\AgV \sim \AgentDist]{%
\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq \delta}$
to be the total probability mass (across all arms) of agents
whose (actual) preference for their best arm over their second-best
arm is at most $\delta$.
}
\dkcomment{We should stress somewhere that we assume that actual ties
  have measure 0.}

@@

We begin by bounding the length of any phase, which will support bounding
the regret of early rounds
(before tail bounds have kicked in). We prove Lemma~\ref{lem:phase-length} in Appendix~\ref{sec:lemma4-proof}.
